---
title: "My Website"
---
## NOTE: www.kylejeffreyreese.com is my new website and the stuff here will be removed.




Welcome! This is my website created with R Markdown (originally a few years ago which is why it needs an upgrade). It's connected with my github account so I can quickly commit and push updates out. It's still a work in progress (I need to update quite a bit).   

One interesting thing that I can do is run R code directly to produce interesting output (with the knitr package I have access to approximately 30 other programming languages too). For example, consider the plot below from the gapminder dataset (a classic!). It displays the change of GDP per capita and life expectancy over time.


```{r, echo = FALSE, message=FALSE}
library(ggplot2)
library(plotly)
```


```{r, echo = TRUE, fig.align='center', message=FALSE}
data(gapminder, package = "gapminder")
gg <- ggplot(gapminder, aes(gdpPercap, lifeExp, color = continent)) +
  geom_point(aes(size = pop, frame = year, ids = country)) +
  scale_x_log10()
ggplotly(gg)

```


There is so much to do! (Like figure out why ggplotly gives me useless warnings)





